### 2011-05-12 paper/paper.tex
added citation about estimating volume

We consider the problem of randomly and uniformly sampling a point from a convex region in $n$-dimensional space. This has applications, for instance, in convex optimization \cite{Dabbene}. We phrase the problem as follows: we are given a convex region $\mathcal{R}$ in the form of a \emph{membership oracle} which determines whether a given point $x$ is in $\mathcal{R}$, along with a starting point $x_0$ in $\mathcal{R}$. The task is to sample a point from the region with with a distribution as close to uniform as possible.

@@

@@

\bibitem{Vempala} Lov\'asz, L. and Vempala, S. Hit-and-Run from a corner. \emph{SIAM Journal on Computing}, 35(4):9851005, 2006.

@@

\bibitem{Smith} Smith, R.L. \emph{Efficient Monte-Carlo procedures for generating points uniformly distributed over
bounded regions}, Oper. Res., 32 (1984), pp. 1296-1308.

>>>>

We consider the problem of randomly and uniformly sampling a point from a convex region in $n$-dimensional space. This has applications, for instance, in convex optimization \cite{Dabbene}. Sampling can also allow us to estimate the volume of a convex region \cite{Dyer}.

We phrase the problem as follows: we are given a convex region $\mathcal{R}$ in the form of a \emph{membership oracle} which determines whether a given point $x$ is in $\mathcal{R}$, along with a starting point $x_0$ in $\mathcal{R}$. The task is to sample a point from the region with with a distribution as close to uniform as possible.

@@

\bibitem{Dyer} Dyer, M.E., Frieze, A.M., and Kannan, R. ``A random polynomial-time algorithm for approximating the volume of convex bodies." Journal of the ACM, 38:1-17, 1991.

@@

\bibitem{Vempala} Lov\'asz, L. and Vempala, S. ``Hit-and-Run from a corner." \emph{SIAM Journal on Computing}, 35(4):9851005, 2006.

@@

\bibitem{Smith} Smith, R.L. ``Efficient Monte-Carlo procedures for generating points uniformly distributed over
bounded regions." Oper. Res., 32 (1984), pp. 1296-1308.
